Generalized Plackett-Luce Likelihoods

### 2022-08-13 inst/jss_hyper3.Rnw
slight rewording

\begin{itemize}
\item $A\succ A\succ B\longrightarrow\frac{a^2}{1+a}$
\item $A\succ B\succ A\longrightarrow\frac{1-2a-a^2}{(1+a)^2}$
\item $B\succ A\succ A\longrightarrow\frac{1-a}{1+a}$
\end{itemize}

Likelihood functions for these order statistics are given in
Figure~\ref{ABAetc_likelihood}.  It can be shown that the Fisher
information for such observations is

@@

which has a minimum at about $0.575$.

@@

If we allow non-finishers---that is, a subset of competitors who are
beaten by all the ranked competitors: \cite{turner2020} call this a
{\em top $n$ ranking}), there is another nontrivial order statistic,
viz $a\succ b\succ\left\lbrace a,b\right\rbrace$ [thus one of the two
  $a$'s won, one of the $b$'s came second, and one of each of $a$ and
  $b$ failed to finish].

>>>>

If we have two clones of $a$ and a singleton $b$, then there are three
possible rank statistics: (i), $a\succ a\succ b$ with probability
$\frac{a^2}{1+a}$; (ii), $a\succ b\succ a$, with
$\frac{1-2a-a^2}{(1+a)^2}$, (iii), $b\succ a\succ a$ at
$\frac{1-a}{1+a}$.  Likelihood functions for these order statistics
are given in Figure~\ref{ABAetc_likelihood}.  It can be shown that the
Fisher information for such observations is

@@

which has a minimum of about $13.9$ at at about $a=0.575$.

@@

If we allow non-finishers---that is, a subset of competitors who are
beaten by all the ranked competitors (\cite{turner2020} call this a
{\em top $n$ ranking}), there is another nontrivial order statistic,
viz $a\succ b\succ\left\lbrace a,b\right\rbrace$ [thus one of the two
  $a$'s won, one of the $b$'s came second, and one of each of $a$ and
  $b$ failed to finish].  Now
